%\pmComment{Incomplete}

The journey of completing this dissertation has been one of many ups and downs, and I am grateful to many people who have supported me along the way.
My advisor, Dr. Srinivasan Parthasarathy, has given me the right impetus for taking the most important step at each stage—the next one. 
He has encouraged me to go beyond my comfort zone and explore new research directions.
His guidance has helped me refine my ideas and thoughts through writing and presentations, which has made me more effective in communicating my research.
Further, he has always encouraged me to pursue interesting external research opportunities through summer internship programs, which have helped shape my research interests and allowed me to apply them in practical settings.
I am grateful for his mentorship and support throughout this process.

I would also like to acknowledge the members of my candidacy and dissertation committees, Dr. Andrew Perrault, Dr. Micha Elsner, Dr. Eric Fosler-Lussier, and Dr. Amy Sheneman, for their valuable feedback, which helped me better situate my research in the broader context of ideas in stylometry, information retrieval, and fairness in machine learning.
In particular, Dr. Micha Elsner provided valuable feedback on the early drafts of my stylometry work, which provided the final nudge to help push the work toward a high-quality publication.
I would also like to thank my mentors before my Ph.D., Dr. Atanu Sinha and Dr. Subhajit Roy, for encouraging me to pursue a Ph.D. and providing me with the proper guidance to transition from a wide-eyed undergraduate student to industry and academia.

Members of the Data Mining Research Group at The Ohio State University at The Ohio State University have been frequent collaborators and confidantes through the process of my Ph.D.
I have had the privilege of working with Dr. Nikhita Vedula, Dr. Bortik Bandyopadhyay, Dr. Saket Gurukar, Dr. Goonmeet Bajaj, Dr. Mark Susmann, Dr. Moniba Keymanesh, Yuntian He, Vedang Patel, Aditya Vadlamani, Sean Current, Anutam Srinivasan, Dominik Winecki, Ram Sai Ganesh, Saumya Sahai, Meghana Moorthy Bhat, Kuan-Chieh Lo, and Yue Zhang, who have been excellent collaborators and friends.
I am grateful for the many discussions, brainstorming sessions, and collaborative projects that have helped me maintain steady progress in the face of challenges.
Through external collaborations and internships, both inside and outside Ohio State, I have also been fortunate to work with Dr. Zhanlong Qiu, Dr. Lanfeng Pan, Dr. Byung-Doh Oh, Dr. Nanjiang Jiang, Dr. Jay Stokes, Dr. Octavian Udrea, Dr. William Groves, Dr. Nicholas Andrews, Dr. Marcus Bishop, Dr. Zachary Lubberts, Dr. Kevin Duh, AlFahad AlQadhi, Roy Siegelmann, Dr. Cristina Aggazzotti, Dr. Dana Haynie, and Dr. Scott Duxbury.

I am also thankful to the National Science Foundation, which has funded my research through grants SES-1949037, CCF-2028944, and \#2112471 (AI-EDGE).
My research would not have been possible without the excellent computing resources supporting  Ohio State Computer Science students, including the MRI cluster (also funded by the NSF through OAC-2018627) and the Ohio Supercomputer Center. 
Cisco's Responsible AI group has graciously provided funding to support my work on fairness auditing.
Any opinions, findings,  conclusions, or recommendations expressed in this material are mine and do not necessarily reflect the views of the National Science Foundation or Cisco.

Finally, I am grateful for having had my wife, Meghana Gupta, who has suffered my (occasional) grumpiness through deadlines and late nights that come with the territory of being a Ph.D. student.
She and our cat Sage have been a constant source of joy and support and have helped me maintain a semblance of balance in my life.
I am also grateful to my parents and sister, who supported my decision to leave a comfortable job in India to pursue a Ph.D. in the United States.
Their encouragement has been invaluable in helping me navigate the challenges of graduate school.
