\chapter{Detecting Phishing URLs using Transformers}
\label{chp:urltran}
%\todo{Add some general information connecting to the broader theme. + Make the introduction more relevant to the thesis.}
%\todo{TODO: Make references local? For figures etc.}

In this chapter, we present our work on phishing URL (Uniform Resource Locator) detection~\citep{maneriker2021urltran} conducted at Microsoft, contextualized within the broader theme of our thesis surrounding the use of structures to build \textit{adversarial testing} for \textit{pre-deployment} robustness. 
We study the problem of detecting phishing URLs using transformer models.

Browsers often include security features to detect phishing web pages. 
In the past, some browsers evaluated unknown URLs for inclusion in lists of known phishing pages.
However, phishing URLs and websites have a very short life span~\citep{garera2007framework,chu2013protect}. 
Therefore, models must be able to \textit{adapt} to rapidly changing data distribution.
As the number of URLs and known phishing pages has continued to increase rapidly, browsers have started to include one or more machine learning classifiers in their security services, which aim to better protect end users from harm.

Recent research has proposed using deep learning models for the phishing URL detection task~\cite{sahoo2017malicious,yerima2020high,ren2019bidirectional,peng2019joint,huang2019phishing,tajaddodianfar2020texception}.
Concurrently, text embedding research using transformers has led to state-of-the-art results in many natural language processing tasks.
In this contribution, we first comprehensively analyze transformer models on the phishing URL detection task.
We consider both pre-trained and end-to-end transformer models, with standard masked language models and additional domain-specific pre-training tasks.
We compare end-to-end training compare against fine-tuned BERT and RoBERTa models.
Misclassifying a benign URL as malicious can be damaging for a phishing URL classification model.%~\cite{TODO}\todo{Fix reference}.
Therefore, phishing URL detection models are compared by measuring true positive rates at very low false positive rates.
 The insights our experiments help us propose \URLTranSys, which uses transformers to significantly improve the performance of phishing URL detection over a wide range of very low false positive rates (FPRs) compared to other deep learning-based methods.
For example, \URLTranSys yields a true positive rate (TPR) of 86.80\% compared to 71.20\% for the next best baseline at an FPR of 0.01\%, resulting in a relative improvement of over 21.9\%.
We use insights from the structure of URL grammar~\cite{rfc3986}.

As mentioned previously, phishing URL attacks are carried out through short-lived and changing URL patterns.
Therefore, the machine learning models must be retrained and redeployed at regular intervals.
This procedure may lead to a \textit{catastrophic forgetting}~\citep{mccloskey1989catastrophic} phenomenon, whereby models forget the old patterns and only adapt to new ones.
In our second contribution to this work, we propose a threat model and construct an \textit{adversarial testing} scenario to validate models against known threat patterns before deployment.
We consider some classical adversarial black-box phishing attacks, such as those based on homoglyphs and compound word splits, to improve the robustness of \URLTranSys.
Inspired by the behavioral testing paradigm~\citep{ribeiro2020beyond}, we provide algorithms to efficiently construct datasets that can help quantify the capabilities of trained models against known threat patterns.
%We consider additional fine tuning with these adversarial samples and demonstrate that \URLTranSys can maintain low FPRs under these scenarios.

\input{urltran/introduction}
\input{urltran/related}
\input{urltran/dataset}
\input{urltran/methodology}
\input{urltran/results}
\input{urltran/conclusion}

\endinput