\dateitem{July 2012 -- June 2016}{B. Tech,\\
Department of Computer Science and Engineering,\\
Indian Institute of Technology, Kanpur, India.}

\dateitem{May 2015 -- July 2015}{Research Intern,\\
Adobe Research, Bengaluru, India.}

\dateitem{Aug 2015 -- Nov 2015}{Teaching Assistant, \\
Data Structures and Algorithms, \\
Indian Institute of Technology, Kanpur, India.}

\dateitem{Jan 2016 -- Apr 2016}{Tutor, \\
Introduction to Programming, \\
Indian Institute of Technology, Kanpur, India.}

\dateitem{June 2016 -- July 2018}{Research Associate,\\
 Adobe Research, Bengaluru, India.}

\dateitem{August 2018 -- present}{Ph.D. student,\\
Department of Computer Science and Engineering,\\
The Ohio State University, Columbus, USA.}

\dateitem{August 2018 -- present}{Graduate Research Associate,\\
Department of Computer Science and Engineering,\\
The Ohio State University, Columbus, USA.}

\dateitem{May 2019 -- August 2019}{Applied Scientist Intern,\\
Amazon, Seattle, USA.}

\dateitem{May 2020 -- August 2020}{Research Intern,\\
Microsoft Research, Redmond, USA.}

\dateitem{May 2021 -- August 2021}{Research Intern,\\
Dataminr Inc., New York, USA.}

\dateitem{June 2022 -- August 2022}{Visiting Research Scholar,\\
Johns Hopkins University HLTCOE, Baltimore, USA.}

\begin{publist}
    \researchpubs

    \pubitem{\textbf{Pranav Maneriker}, Codi Burley, Srinivasan Parthasarathy, "Online Fairness Auditing trhough Iterative Refinement", In \emph{Proceedings of the 29th ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD)}, 2023.}
    \pubitem{Saket Gurukar, Priyesh Vijayan, Srinivasan Parthasarathy, Balaraman Ravindran, Aakash Srinivasan, Goonmeet Bajaj, Chen Cai, Moniba Keymanesh, Saravana Kumar, \textbf{Pranav Maneriker}, Anasua Mitra, Vedang Patel, "Benchmarking and Analyzing Unsupervised Network Representation Learning and the Illusion of Progress", In \emph{Transactions of Machine Learning Research (TMLR)}, 2022.}
    \pubitem{\textbf{Pranav Maneriker}, Yuntian He, Srinivasan Parthasarathy, "SYSML: StYlometry with Structure and Multitask Learning: Implications for Darknet Forum Migrant Analysis", In \emph{Proceedings of the 2021 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, 2021.}
    \pubitem{\textbf{Pranav Maneriker}, Jack W Stokes, Edir Garcia Lazo, Diana Carutasu, Farid Tajaddodianfar, Arun Gururajan, "URLTran: Improving Phishing URL Detection Using Transformers", In \emph{Proceedings of IEEE Military Communications Conference (MILCOM)}, 2021.}
    \pubitem{Bortik Bandyopadhyay, \textbf{Pranav Maneriker}, Vedang Patel, Saumya Yashmohini Sahai, Ping Zhang, Srinivasan Parthasarathy, "DrugDBEmbed: Semantic Queries on Relational Database using Supervised Column Encodings", In \emph{arXiv preprint arXiv:2007.02384}, 2020.}
    \pubitem{Nikhita Vedula, Nedim Lipka, \textbf{Pranav Maneriker}, Srinivasan Parthasarathy, "Open Intent Extraction from Natural Language Interactions", In \emph{Proceedings of The Web Conference (WWW)}, 2020.}
    \pubitem{Goonmeet Bajaj, Bortik Bandyopadhyay, Daniel Schmidt, \textbf{Pranav Maneriker}, Christopher Myers, Srinivasan Parthasarathy, "Understanding Knowledge Gaps in Visual Question Answering: Implications for Gap Identification and Testing", In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition Workshops}, 2020.}
    \pubitem{Ritwick Chaudhry, Sumit Shekhar, Utkarsh Gupta, \textbf{Pranav Maneriker}, Prann Bansal, Ajay Joshi, "LEAF-QA: Locate, Encode \& Attend for Figure Question Answering", In \emph{Proceedings of the IEEE/CVF Winter Conference on Applications of Computer Vision (WACV)}, 2020.}
    \pubitem{Byung-Doh Oh, \textbf{Pranav Maneriker}, Nanjiang Jiang, "THOMAS: The Hegemonic OSU Morphological Analyzer using Seq2seq", In \emph{Proceedings of the 16th Workshop on Computational Research in Phonetics, Phonology, and Morphology (SIGMORPHON)}, 2019.}
    \pubitem{\textbf{Pranav Maneriker}, Nikhita Vedula, Hussein S Al-Olimat, Jiayong Liang, Omar El-Khoury, Ethan Kubatko, Desheng Liu, Krishnaprasad Thirunarayan, Valerie Shalin, Amit Sheth, Srinivasan Parthasarathy, "A Pipeline for Disaster Response and Relief Coordination", In \emph{Proceedings of the 42nd International ACM SIGIR Conference on Research and Development in Information Retrieval}, 2019.}
    \pubitem{Nikhita Vedula, \textbf{Pranav Maneriker}, Srinivasan Parthasarathy, "BOLT-K: Bootstrapping Ontology Learning via Transfer of Knowledge", In \emph{Proceedings of The World Wide Web Conference (WWW)}, 2019.}
    \pubitem{Paridhi Maheshwari, Nitish Bansal, Surya Dwivedi, Rohan Kumar, \textbf{Pranav Maneriker}, Balaji Vasan Srinivasan, "Exemplar based Experience Transfer, In \emph{Proceedings of the 24th International Conference on Intelligent User Interfaces (IUI)}, 2019.}
    \pubitem{Ritwik Sinha, Dhruv Singal, \textbf{Pranav Maneriker}, Kushal Chawla, Yash Shrivastava, Deepak Pai, Atanu R Sinha, "Forecasting Granular Audience Size for Online Advertising", In \emph{Proceedings of the AdKDD}, 2019.}
    \pubitem{Balaji Vasan Srinivasan, \textbf{Pranav Maneriker}, Kundan Krishna, Natwar Modani, "Corpus-based Content Construction", In \emph{Proceedings of the 27th International Conference on Computational Linguistics (COLING)}, 2018.}
    \pubitem{Gaurush Hiranandani, \textbf{Pranav Maneriker}, Harsh Jhamtani, "Generating Appealing Brand Names", In \emph{Proceedings of the 18th International Conference of Computational Linguistics and Intelligent Text Processing (CICLing)}, 2018.}
    \pubitem{Atanu R. Sinha, Meghanath Macha, \textbf{Pranav Maneriker}, Sopan Khosla, Avani Samdariya, Navjot Singh, "Anti-Ad Blocking Strategy: Measuring Its True Impact", In \emph{Proceedings of the AdKDD}, 2017.}
    \pubitem{Natwar Modani, \textbf{Pranav Maneriker}, Gaurush Hiranandani, Atanu R Sinha, Utpal, Vaishnavi Subramanian, Shivani Gupta, "Summarizing Multimedia Content", In \emph{Web Information Systems Engineering (WISE)}, 2017.}

    \patentpubs
    \pubitem{\textbf{Pranav Maneriker}, Codi Burley, Srinivasan Parthasarathy, "Systems and Methods for Measuring and Auditing Fairness", \emph{US Patent App. No. 18/419,130}, 2024.}
    \pubitem{Jack Wilson Stokes III, \textbf{Pranav Maneriker}, Arunkumar Gururajan, Diana Anca Carutasu, Edir Vinicio Garcia Lazo, "Phishing URL Detection using Transformers", \emph{US Patent App. No. 17/246,352}, 2022.}
    \pubitem{Ritwik Sinha, Virgil-Artimon Palanciuc, \textbf{Pranav Maneriker}, Manish Dash, Tharun Mohandoss, Dhruv Singal, "Accurate and interpretable rules for user segmentation", \emph{US Patent No. 11,200,501}, 2021.}
    \pubitem{\textbf{Pranav Maneriker}, Reshmi Sasidharan, Atanu R. Sinha, "Facilitating changes to online computing environment by assessing impacts of temporary interventions", \textit{US Patent No. 11,038,785}, 2021.}
    \pubitem{\textbf{Pranav Maneriker}, Vishwa Vinay, Sopan Khosla, Niyati Himanshu Chhaya, Natwar Modani, Cedric Huesler, Balaji Vasan Srinivasan, Anandhavelu Natarajan, "Fact Replacement and Style Consistency Tool", \emph{US Patent No. 11,194,958}, 2021.}
    \pubitem{Atanu R Sinha, Meghanath Macha Yadagiri, \textbf{Pranav Maneriker}, Sopan Khosla, Avani Samdariya, Navjot Singh, "Techniques to quantify effectiveness of site-wide actions", \emph{US Patent No. 11,093,957}, 2021.}
    \pubitem{Balaji Vasan Srinivasan, \textbf{Pranav Maneriker}, Natwar Modani, Kundan Krishna, "Constructing Content based on Multi-sentence Compression of Source Content", \emph{US Patent No. 10,949,452} 2021.}
    \pubitem{Ritwik Sinha, \textbf{Pranav Maneriker}, Dhruv Singal, Atanu R Sinha, "Identifying High Value Segments in Categorical Data", \emph{US Patent No. 10,929,438}, 2021.}
    \pubitem{Balaji Vasan Srinivasan, Shiv Kumar Saini, Kundan Krishna, Anandhavelu Natarajan, Tanya Goyal, \textbf{Pranav Maneriker}, Cedric Huesler, "Bundling Online Content Fragments for Presentation based on Content-Specific Metrics and Inter-Content Constraints", \emph{US Patent No. 10,891,667}, 2021.}
    \pubitem{Balaji Vasan Srinivasan, Surya S Dwivedi, Rohan Kumar,\textbf{Pranav Maneriker}, Paridhi Maheshwari, Nitish Bansal, "Techniques for Generating Templates from Reference Single Page Graphic Images", \emph{US Patent App. No. 16/376,906}, 2021.}
    \pubitem{Natwar Modani, Vaishnavi Subramanian, Shivani Gupta, \textbf{Pranav Maneriker}, Gaurush Hiranandani, Atanu Sinha, "Multimedia Document Summarization", \emph{US Patent No. 10,762,283}, 2021.}
    \pubitem{Pranav Ravindra Maneriker, Anandhavelu Natarajan, Vivek Gupta, "Predicting Style Breaches within Textual Content", \emph{US Patent No. 10,650,094}, 2021.}
    \pubitem{Natwar Modani, Vaishnavi Subramanian, Shivani Gupta, Pranav Ravindra Maneriker, Gaurush Hiranandani, Atanu R Sinha, "Determining quality of a summary of multimedia content", \emph{US Patent No. 9,454,524}, 2016}
\end{publist}
\pmComment{Only post PhD pubs?}


\begin{fieldsstudy}
    \majorfield{Computer Science and Engineering}
    \begin{studieslist}
        \studyitem{Data Mining}{Dr. Srinivasan Parthasarathy}
        \studyitem{Computational Linguistics}{Dr. Micha Elsner}
        \studyitem{Optimization}{Dr. Abhishek Gupta}
    \end{studieslist}
\end{fieldsstudy}