\subsection{\AVOIRmethodname{}: Key Contributions}
\label{sec:contributions}

We now summarize our contributions vis-à-vis FP and Verifair.
(1) We build up \AVOIRmethodname{} in the framework of \textbf{confidence sets}~\citep{howard2021time} which enables the \textbf{adaptive optimization} of $\delta$ across subexpressions.
Note that FP provides examples with equal splits across two terms though it makes no specific prescription of splits.
Verifair splits uncertainty equally across all elementary subexpressions.
(2) The confidence sets framework allows us to move away from assuming a known data distribution or alternatively, fitting a density estimator over the population prior to fairness testing, required in Verifair.
(3) We augment the \textbf{bound propagation rules} to facilitate the online optimization process and allow propagation of constraints along with assertions at each iteration.
\todo{New contributions section.}
(4) We build an \textbf{inference engine} that supports automated inference of propagation rules for wide range of metrics.
In Section~\ref{sec:casestudy}, we provide examples of inference over specifications involving over two subexpressions, which are not possible without extending the implementations provided by previous work. 
As a baseline, we also implement bound inference rules from Verifair (denoted \AVOIRmethodname{}-VF).
(5) We support \textbf{interactive diagnosis} of fairness specification violations using visual cues associated with convergence of subexpressions.
We demonstrate the use of these cues to help drive the design of specifications in Section~\ref{sec:casestudy:adult}, which show how a user may have audited their original claim and refined mathematical bounds.
%More details about the differences referenced above are also available in Appendix~\ref{sec:appendix:contributions}.